### 2014-06-26 6/conclusional_discussion.tex
auto

Corresponding to the objectives outlined in Chapter 1,
  the following results have been obtained:
\begin{enumerate}
\item           Several scalar and highly representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data have been proposed:
                \begin{enumerate}
                \item The determinant statistical model is established for the determinant of POLSAR covariance matrices (Section \ref{sec:polsar_heterosked_model_and_log_transform}),
                \item Several statistical models for different discrimination measures (namely: determinant-ratio, log-distance, dispersion and contrast) are derived together with its consistent property (Section \ref{sec:consistent_measures_distance_polsar}). %being modelled 
                \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
                \item \label{itm:polsar_validation} The proposed models are validated against practical real-life
                captured POLSAR data in Section \ref{sec:polsar_models_validation}.
                \end{enumerate}
\item                Homoskedastic statistical models for the
                heteroskedastic (POL)SAR data are derived. Specifically 
                \begin{enumerate}
                \item \label{itm:log_transform} The statistical model for POLSAR data are shown to be heteroskedastic in
                the original domain and logarithmic transformation
                converts this into a homoskedastic model (Sections: \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data are derived (Sections: \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
                \item \label{itm:sar_validation} These statistical models are validated against both
                practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
                \end{enumerate}
\item The beneficial applications of these
                statistical models have also been demonstrated. Specifically:
                \begin{enumerate}
                \item \label{itm:filter_vicious_circle} The consistent sense of variance
                is shown to help breaking the vicious cycle in the problem of SAR
                speckle filtering: with new statistical test for
                homogeneity and new speckle filters proposed (Sections: \ref{sec:k_mle}, \ref{sec:f_mle}).
                \item \label{itm:log_mse} The consistent sense of subtractive
                distance also helps in the problem of evaluating SAR
                speckle filters. Section \ref{sec:sar_filters_evaluation} proposes the use of the log-MSE to combine the
                evaluation of radiometric preservation and speckle
                suppression power in evaluating SAR speckle filters.
                \item \label{itm:extend_sar_to_polsar} Sections \ref{sec:polsar_models_validation} and \ref{sec:polsar_speckle_filters_evaluation} demonstrate several instances where existing SAR
                processing techniques are extended towards POLSAR data.
                \end{enumerate}
\end{enumerate}

@@

At
                the same time, a consistently meaningful sense of
                distance leading to our proposal of using the familiar
                MSE in the homoskedastic domain to evaluate SAR speckle
                filters.
Intuitively,
                this comes about as the speckle suppression power of
                speckle filters can be evaluated via variance estimation
                practice, while the radiometric preservation can be
                evaluated via the normal bias evaluation.
Combined,
                while there are many different evaluation criteria in
                the heteroskedastic SAR speckle filter evaluation
                framework, the MSE is proposed as the single unified
                evaluation criteria for SAR speckle filters.
In
                short, it is shown that in the homoskedastic domain, not
                only it is possible to find the equivalent of existing
                methods overcoming heteroskedastic drawbacks in the
                original domain, it is also possible to suggests further
                improvements based on existing techniques.

The
                proposed models for POLSAR also bring forward several
                important benefits.
Since
                the models, especially those for discrimination
                measures, can be considered as the multidimensional
                extension of the models for SAR, it makes many existing
                SAR processing techniques extensible towards POLSAR
                data.
The POLSAR determinant ratio, for example, can be considered as
                the extension of the ubiquitous SAR intensity ratio.
This
                thesis also illustrates how the MSE evaluation
                criteria can also be extended from SAR to POLSAR.

>>>>

Corresponding to the objectives outlined in Chapter 1,
  the following results have been obtained:
\begin{enumerate}
\item           Several scalar and highly representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data have been proposed:
                \begin{enumerate}
                \item The determinant statistical model is established for the determinant of POLSAR covariance matrices (Section \ref{sec:polsar_heterosked_model_and_log_transform}),
                \item Several statistical models for different discrimination measures (namely: determinant-ratio, log-distance, dispersion and contrast) are derived together with its consistent property (Section \ref{sec:consistent_measures_distance_polsar}). %being modelled 
                \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
                \item The proposed models are validated against practical real-life
                captured POLSAR data in Section \ref{sec:polsar_models_validation}.
                \end{enumerate}
\item                Homoskedastic statistical models for the
                heteroskedastic (POL)SAR data are derived. Specifically 
                \begin{enumerate}
                \item The statistical model for POLSAR data are shown to be heteroskedastic in
                the original domain and logarithmic transformation
                converts this into a homoskedastic model (Sections: \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
                \item Homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data are derived (Sections: \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
                \item These statistical models are validated against both
                practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
                \end{enumerate}
\item The beneficial applications of these
                statistical models have also been demonstrated. Specifically:
                \begin{enumerate}
                \item The consistent sense of variance
                is shown to help breaking the vicious cycle in the problem of SAR
                speckle filtering: with new statistical test for
                homogeneity and new speckle filters proposed (Sections: \ref{sec:k_mle}, \ref{sec:f_mle}).
                \item The consistent sense of subtractive
                distance also helps in the problem of evaluating SAR
                speckle filters. Section \ref{sec:sar_filters_evaluation} proposes the use of the log-MSE to combine the
                evaluation of radiometric preservation and speckle
                suppression power in evaluating SAR speckle filters.
                \item  Sections \ref{sec:polsar_models_validation} and \ref{sec:polsar_speckle_filters_evaluation} demonstrate several instances where existing SAR
                processing techniques are extended towards POLSAR data.
                \end{enumerate}
\end{enumerate}

@@

At
                the same time, a consistently meaningful sense of
                distance leading to our proposal of using the familiar
                MSE in the homoskedastic domain to evaluate SAR speckle
                filters.
Intuitively,
                this comes about as the speckle suppression power of
                speckle filters can be evaluated via variance estimation
                practice, while the radiometric preservation can be
                evaluated via the normal bias evaluation.
Combined,
                while there are many different evaluation criteria in
                the heteroskedastic SAR speckle filter evaluation
                framework, the MSE is proposed as the single unified
                evaluation criterion for SAR speckle filters.
In
                short, it is shown that in the homoskedastic domain, not
                only it is possible to find the equivalent of existing
                methods overcoming heteroskedastic drawbacks in the
                original domain, it is also possible to suggests further
                improvements based on existing techniques.

The
                proposed models for POLSAR also bring forward several
                important benefits.
Since
                the models, especially those for discrimination
                measures, can be considered as the multidimensional
                extension of the models for SAR, it makes many existing
                SAR processing techniques extensible towards POLSAR
                data.
The POLSAR determinant ratio, for example, can be considered as
                the extension of the ubiquitous SAR intensity ratio.
This
                thesis also illustrates how the MSE evaluation
                criterion can also be extended from SAR to POLSAR.
